Live Functional Programming with Typed Holes

### 2018-04-17 fig-grades-example.tex
added mockup

\begin{lstlisting}
type student_data =
  { name: string, 
    hw1: float, hw2: float, hw3: float, 
    midterm: float, final: float };

let grades : list(student_data) =
  [ { name: "Alice", hw1: 76.0, hw2: 93.0, hw3: 91.0, midterm: 77.0, final: 95.0 }
  , { name: "Bob"  , hw1: 88.0, hw2: 75.0, hw3: 80.0, midterm: 89.0, final: 87.0 }
  ];
\end{lstlisting}

\rkc{Place this code fragment (and some pieces of the subsequent fragments) in a
single mockup or screenshot.}

\caption{\rkc{...}}
\label{fig:grades-example}
\end{figure}

>>>>

\includegraphics[width=1.01\textwidth,interpolate=false]{images/grades-cell-mockup.png}

% %% TODO once the code above is removed, scale up the screenshots
% \includegraphics[scale=0.20]{images/hazel-placeholder-0.png}

% \rkc{Draw arrows and captions on the top figure to show how to get
% to the bottom figure.
% ser navigates to hole a, types + to create a plus, types * to create a
% multiplication, types \#10 to create 10, types vh1 to create variable use.}

% \includegraphics[scale=0.20]{images/hazel-placeholder-1a.png}

\caption{Hazel mockups for Example 1a.}
\label{fig:grades-example}
\end{figure}
